On the Dynamics of Anthropomorphism in Robotics

### 2013-06-26 dynamics-anthropomorphism.tex
Amended the introduction

\author{Julia Fink, Séverin Lemaignan, Pierre Dillenbourg}
\affiliation{ Computer-Human Interaction in Learning and Instruction (CHILI) \\
              Ecole Polytechnique Fédérale de Lausanne (EPFL) \\
              CH-1015 Lausanne, Switzerland
}
\abstract{While anthropomorphism in robotics is a commonly discussed trait of HRI, it is paradoxically an overlooked research topic. This article attempts first at providing a comprehensive synthesis of the social phenomenon of \textit{perceiving human-like characteristics in non-human agents and attributing those characteristics to robots}. We draw on social sciences and psychology, as well as on a critical survey of existing literature in the HRI community, to ground the concept of \textit{anthropomorphism}. We further briefly present different kinds of \textit{anthropomorphic design} of robots and outline their role in social robotics. We then propose to go beyond the traditional perception of anthropomorphism as a static feature. We suggest to understand anthropomorphism as a dynamic, context-dependent process, which changes over time. This also provides an account of the so-called \textit{novelty effect}. To this end, we introduce an initial function of anthropomorphism that models the phenomenon along three interaction phases. Our function is supported by results of a long-term study that we conducted in a real human environment.}

>>>>

\author{Julia Fink, Séverin Lemaignan, Pierre Dillenbourg}
\affiliation{ Computer-Human Interaction in Learning and Instruction (CHILI) \\
              Ecole Polytechnique Fédérale de Lausanne (EPFL) \\
              CH-1015 Lausanne, Switzerland
}

\abstract{While anthropomorphism in robotics is a commonly discussed trait of
HRI, it is paradoxically an overlooked research topic. This article
attempts first at providing a comprehensive synthesis of the social
phenomenon of \textit{perceiving human-like characteristics in non-human
agents and attributing those characteristics to robots}. We draw on
social sciences and psychology, as well as on a critical survey of
existing literature in the HRI community, to ground the concept of
\textit{anthropomorphism}. We further briefly present different kinds
of \textit{anthropomorphic design} of robots and outline their role in
social robotics\fxfatal{do we really do?}. We then suggest to go beyond the traditional
perception of anthropomorphism as a static feature of a system: we propose to
understand anthropomorphism as a dynamic, non-monotonic and
context-dependent process, which evolves over time and accounts for
special events like the so-called \textit{novelty effect}. To this end,
we introduce a model of anthropomorphism that analyzes the phenomenon
along three interaction phases. These findings are supported by a long-term
study conducted in a real human environment.}
